P versus NP

### 2019-11-25 doc/manuscript.tex
Updated finally the content proof

If $L_{1}$ is a language such that $L' \leq_{p} L_{1}$ for some $L' \in \textit{coNP--complete}$, then $L_{1}$ is $\textit{coNP--hard}$ \cite{CLRS01}. Moreover, if $L_{1} \in coNP$, then $L_{1} \in \textit{coNP--complete}$ \cite{CLRS01}. A principal $\textit{coNP--complete}$ problem is $UNSAT$ \cite{GJ79}. A formula without any satisfying truth assignment is an unsatisfiable formula. The problem $UNSAT$ asks whether a given Boolean formula is unsatisfiable \cite{GJ79}.

@@

INSTANCE: A collection of integers (positive or negative) $C$ such that $0 \notin C$ and every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$ (we fill with zeroes to the left the elements in case of necessity).

QUESTION: Are there two elements $a, b \in C$ such that $a + b = 0$?

>>>>

If $L_{1}$ is a language such that $L' \leq_{p} L_{1}$ for some $L' \in \textit{coNP--complete}$, then $L_{1}$ is $\textit{coNP--hard}$ \cite{CLRS01}. Moreover, if $L_{1} \in coNP$, then $L_{1} \in \textit{coNP--complete}$ \cite{CLRS01}. A principal $\textit{coNP--complete}$ problem is $UNSAT$ \cite{GJ79}. A Boolean formula without any satisfying truth assignment is unsatisfiable. The problem $UNSAT$ asks whether a given Boolean formula is unsatisfiable \cite{GJ79}.

@@

INSTANCE: A collection of integers $C$ such that $0 \notin C$ and every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$ (we do not take into account the symbol minus in the bit-length of the negative integers).

QUESTION: Are there two elements $a, b \in C$, such that $a + b = 0$?
